Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-15 bbbq_article.tex
Remove keyword 'SARS-CoV-2', thanks Geert, progress #179

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, SARS-CoV-2, evolutionary conservation

>>>>

{\bf Keywords:} antigen presentation, membrane proteins, bioinformatics, 
adaptive immunity, transmembrane domain, transmembrane helix, 
epitopes, T lymphocyte, MHC-I, MHC-II, evolutionary conservation
